### 2019-09-25 paper/paper.tex
Update paper.tex

\usepackage{hyperref}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{graphicx}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{subcaption}
\usepackage{todonotes}
\usepackage{amsmath}
\usepackage{etoolbox}
\usepackage{comment}
\usepackage{minted}

\setminted[Julia]{
    fontfamily=fdm,
    fontsize=\footnotesize,
    escapeinside=||,mathescape=true
    }

@@

\begin{minted}{Julia}
using Pkg
Pkg.add("Zygote")
Pkg.add("ForwardDiff")
using Zygote, ForwardDiff

function s(x) 
    t = 0.0
    sign = -1.0 
    for i in 1:19   
        if isodd(i)
            newterm = x^i/factorial(i)
            abs(newterm)<1e-8 && return t
            println("i=",i)
            sign = -sign
            t += sign * newterm
        end
    end
    return t 
end
\end{minted}

@@

\begin{minted}{Julia}
julia> # Forward Mode AD

@@

julia> cos(1.0)
0.5403023058681398 
\end{minted}

@@

\begin{figure}
    \begin{minipage}{0.5\textwidth}
    \begin{minted}[
    framesep=2mm,
    ]{Julia}
    function |$\mathcal{J}$|(|$f \circ g$|)(x)
        |$a$|, |$\underline{a}$| = |$\mathcal{J}(f)(x)$|
        |$b$|, |$\underline{b}$| = |$\mathcal{J}(g)(a)$|
        |$b$|, |$z$| |$\to$| begin
            |$\underline{a}$($\underline{b}$(z))|
        end
    end
    \end{minted}
    % \begin{verbatim}
    % function J(f . g)(x)
    %     a, da = J(f)(x)
    %     b, db = J(g)(a)
    %     b, z -> da(db(z))
    % end
    % \end{verbatim}
    \caption{The differential operator $\mathcal{J}$ is able to implement the chain rule through a local, syntactic recursive transformation.}\label{chain}
    \end{minipage}
    \hspace{0.1in}
    \begin{minipage}{0.5\textwidth}
    \begin{minted}[
    framesep=2mm,
    fontsize=\footnotesize,
    fontfamily=fdm,
    xleftmargin=6pt,
    escapeinside=||,mathescape=true
    ]{Julia}
    julia> f(x) = x^2 + 3x + 1
    julia> gradient(f, 1/3)
    (3.6666666666666665,)

    julia> using Measurements;
    julia> gradient(f, 1/3 +- 0.01)
    (3.6666666666666665 +- 0.02,)
    \end{minted}
    \caption{With two minimal definitions, \Zygote\ is able to obtain derivatives of any function that only requires those definitions, even through custom data types (such as \textit{Measurement}) and many layers of abstraction.}\label{generalize}
    \end{minipage}
\end{figure}

@@

% \begin{verbatim}
\begin{minted}{Julia}
alphabet, Xs, Ys = load_data("shakespeare_input.txt")

@@

  # Calculate gradients upon the model for this
  # batch of data, summing crossentropy loss
  # across each time index in this batch.
  grads = |\Zygoteplain|.gradient(model) do model
    return sum(crossentropy.(model.(x_batch), y_batch))
  end

  # Update the model, then reset its internal
  # LSTM states
  model = update!(opt, model, grads)
  Flux.reset!(model)
end
\end{minted}
% \end{verbatim}

@@

\begin{minted}{Julia}
guess = PointLight(Vec3(1.0),
                   20000.0,
                   Vec3(1.0, 2.0, -7.0))

@@

gs = gradient(x -> loss_function(x, image), guess) 
\end{minted}

@@

\begin{figure}
    \begin{minipage}{0.48\textwidth}
    \begin{minted}{Julia}
    using Yao, Zygote
    const nsites = 4
    let H = heisenberg(nsites),
        v0 = statevec(zero_state(nsites))
        energy(circuit) =
           (|$\Psi$| = circuit*v0;
            real(|$\Psi'$| * H * |$\Psi$|))
    end
    circuit_init =
        random_diff_circuit(nsites, 2)
    optimize_plot_loss(
        energy, circuit_init, ADAM(0.1))
    \end{minted}
  \caption{An ADAM optimizer is used to tune parameters of a variational quantum circuit to find the ground state of a 4-site anti-ferromagnetic Heisenberg chain Hamiltonian. The necessary gradients are obtained by automatic differentiation of a Yao.jl quantum simulator.}
\end{minipage}
\minipage{0.48\textwidth}
  \includegraphics[width=\linewidth]{images/yao_loss_plot.png}
  \caption{Optimization progress over steps of the classical optimizer to ground state.\label{fig:yao_loss}}
\endminipage
\end{figure}

@@

\begin{minted}[
    frame=lines,
    framesep=2mm,
    fontsize=\footnotesize,
    fontfamily=fdm,
    xleftmargin=6pt,
    escapeinside=||,mathescape=true
    ]{Julia}
julia> guess = PointLight(Vec3(1.0), 20000.0, Vec3(1.0, 2.0, -7.0))

@@

julia> gs = gradient(x -> loss_function(x, image), guess)   
\end{minted}

>>>>

\usepackage{hyperref}
% \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{graphicx}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{subcaption}
% \usepackage{todonotes}
\usepackage{amsmath}
\usepackage{etoolbox}
% \usepackage{comment}
% \usepackage{minted}
\usepackage{listings}

% \setminted[Julia]{
%     fontfamily=fdm,
%     fontsize=\footnotesize,
%     escapeinside=,mathescape=true
%     }

\lstset{language=Julia,mathescape=true}

@@

\begin{lstlisting}
using Pkg
Pkg.add("Zygote")
Pkg.add("ForwardDiff")
using Zygote, ForwardDiff

function s(x) 
    t = 0.0
    sign = -1.0 
    for i in 1:19   
        if isodd(i)
            newterm = x^i/factorial(i)
            abs(newterm)<1e-8 && return t
            println("i=",i)
            sign = -sign
            t += sign * newterm
        end
    end
    return t 
end
\end{lstlisting}

@@

\begin{lstlisting}{Julia}
julia> # Forward Mode AD

@@

julia> cos(1.0)
0.5403023058681398 
\end{lstlisting}

@@

\begin{figure}
    \begin{minipage}{0.5\textwidth}
    \begin{lstlisting}[
    framesep=2mm,
    ]{Julia}
    function $\mathcal{J}$($f \circ g$)(x)
        $a$, $\underline{a}$ = $\mathcal{J}(f)(x)$
        $b$, $\underline{b}$ = $\mathcal{J}(g)(a)$
        $b$, $z$ $\to$ begin
            $\underline{a}$($\underline{b}$(z))
        end
    end
    \end{lstlisting}
    % \begin{verbatim}
    % function J(f . g)(x)
    %     a, da = J(f)(x)
    %     b, db = J(g)(a)
    %     b, z -> da(db(z))
    % end
    % \end{verbatim}
    \caption{The differential operator $\mathcal{J}$ is able to implement the chain rule through a local, syntactic recursive transformation.}\label{chain}
    \end{minipage}
    \hspace{0.1in}
    \begin{minipage}{0.5\textwidth}
    \begin{lstlisting}[
    framesep=2mm,
    fontsize=\footnotesize,
    fontfamily=fdm,
    xleftmargin=6pt,
    escapeinside=,mathescape=true
    ]{Julia}
    julia> f(x) = x^2 + 3x + 1
    julia> gradient(f, 1/3)
    (3.6666666666666665,)

    julia> using Measurements;
    julia> gradient(f, 1/3 +- 0.01)
    (3.6666666666666665 +- 0.02,)
    \end{lstlisting}
    \caption{With two minimal definitions, \Zygote\ is able to obtain derivatives of any function that only requires those definitions, even through custom data types (such as \textit{Measurement}) and many layers of abstraction.}\label{generalize}
    \end{minipage}
\end{figure}

@@

% \begin{verbatim}
\begin{lstlisting}{Julia}
alphabet, Xs, Ys = load_data("shakespeare_input.txt")

@@

  # Calculate gradients upon the model for this
  # batch of data, summing crossentropy loss
  # across each time index in this batch.
  grads = \Zygoteplain.gradient(model) do model
    return sum(crossentropy.(model.(x_batch), y_batch))
  end

  # Update the model, then reset its internal
  # LSTM states
  model = update!(opt, model, grads)
  Flux.reset!(model)
end
\end{lstlisting}
% \end{verbatim}

@@

\begin{lstlisting}{Julia}
guess = PointLight(Vec3(1.0),
                   20000.0,
                   Vec3(1.0, 2.0, -7.0))

@@

gs = gradient(x -> loss_function(x, image), guess) 
\end{lstlisting}

@@

\begin{figure}
    \begin{minipage}{0.48\textwidth}
    \begin{lstlisting}{Julia}
    using Yao, Zygote
    const nsites = 4
    let H = heisenberg(nsites),
        v0 = statevec(zero_state(nsites))
        energy(circuit) =
           ($\Psi$ = circuit*v0;
            real($\Psi'$ * H * $\Psi$))
    end
    circuit_init =
        random_diff_circuit(nsites, 2)
    optimize_plot_loss(
        energy, circuit_init, ADAM(0.1))
    \end{lstlisting}
  \caption{An ADAM optimizer is used to tune parameters of a variational quantum circuit to find the ground state of a 4-site anti-ferromagnetic Heisenberg chain Hamiltonian. The necessary gradients are obtained by automatic differentiation of a Yao.jl quantum simulator.}
\end{minipage}
\minipage{0.48\textwidth}
  \includegraphics[width=\linewidth]{images/yao_loss_plot.png}
  \caption{Optimization progress over steps of the classical optimizer to ground state.\label{fig:yao_loss}}
\endminipage
\end{figure}

@@

\begin{lstlisting}[
    frame=lines,
    framesep=2mm,
    fontsize=\footnotesize,
    fontfamily=fdm,
    xleftmargin=6pt,
    escapeinside=,mathescape=true
    ]{Julia}
julia> guess = PointLight(Vec3(1.0), 20000.0, Vec3(1.0, 2.0, -7.0))

@@

julia> gs = gradient(x -> loss_function(x, image), guess)   
\end{lstlisting}
